---
title       : Letter Cloud and Prediction
subtitle    : A shiny app predicts your love of letters
author      : Z Hao
job         : Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## What do you know about your love of letters?

>1. Most of us know what words are our favorite
  + good
  + chocolate
  + love
  + owesome
>2. And we know letters form words
>3. But our favorite letters are hidden somewhere in our brain.
>4. Let's find them out with this app!

--- 

## Step 1

Give me a list of words that you like:

For example:
```{r}
favorite.words <- c("Good", "Luck", "Owesome", "Serious", "Play", "Fun", "Fine", "Chocolate")
```
Then, type them out:
```{r} 
paste(favorite.words, collapse = " ")
```

---

## Step 2

You then give the sentence to the Letter Cloud app.  
It first chops the words into letters:
```{r}
unlist(strsplit(toupper(favorite.words), NULL))
```
Then create a frequency table from the letters:
```{r, echo=FALSE}
ftable <- table(unlist(strsplit(toupper(favorite.words), NULL)))
ftable
```

---

## Step 3

Finally, the letters are sorted and filtered:
```{r, echo=FALSE}
vletters <- sort(rowSums(as.matrix(ftable)), decreasing = TRUE) 
vletters <- vletters[names(vletters) %in% LETTERS] 
vletters
```
Now we know what your favorite letters are. In this example, it is "`r names(vletters[vletters==max(vletters)])`". 

---
## A quick map of your brain of letters - Letter Cloud
Here is a letter cloud map. Is this your brain of letters?  
Visit [https://prizmworkshop.shinyapps.io/WordCount/][id] for details!  

```{r,echo=FALSE}
library(wordcloud)
wordcloud(names(vletters), vletters, scale=c(8,0.3), min.freq = 1, colors=brewer.pal(8, "Dark2"))   
```

[id]: https://prizmworkshop.shinyapps.io/WordCount/ 
